Ice sheet mass flows

### 2025-08-22 sankey.tex
Increase Sankey label font size

    \newcommand\labelleft[1]{ % valname
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=-3mm]#1.center) {\Lab{v#1}: \qq{#1}};
    }
    \newcommand\labelright[2]{ % valname
      \node[font=\tiny, anchor=west]
      at ([yshift=0mm,xshift=3mm]#1.center) {\qq{#1}: \Lab{#2}};
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vGZRET}/GZ, \Q{vBMB}/BMB}
    }{ % mass gain edge case (AQ_east)
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vGZRET}/GZ, \Q{vBMB}/BMB, \Q{vMG}/MG}
    }
    \sankeyturnleft{RFZo}{1}
    \sankeydubins[minimum radius=5mm,ice-to-water-vert]{RFZo}{RFZi}
    \node[font=\tiny, anchor=east]
           at ([yshift=+1.5mm,xshift=1mm]RFZo.north) {\Lab{vRFZ}: \qq{RFZi}};

@@

    %% SMB outputs
    \sankeynode{name=RUEVa, quantity=\qq{RUEV}, at={[yshift=\yoff]CALVa.left}, anchor=right}
    \sankeyoutin[ice-to-water]{RUEV}{RUEVa}
    \sankeyfork{RUEVa}{\Q{vEV}/EV, \Q{vRU}/RU}
    \sankeynode{name=EVa, quantity=\qq{EV},
      at={[yshift=\yoff,xshift=5mm]RUEVa.left}, anchor=left, angle=45}
    \sankeyoutin[water-to-air]{EV}{EVa}; \sankeyadvance[air]{EVa}{1mm}
    \sankeyend[air]{EVa};
    \node[font=\tiny, anchor=west] at ([yshift=0mm,xshift=\yoff]EVa.west) {\qq{EVa}: \Lab{vEV}};

@@

    \sankeynode{name=SUa, quantity=\qq{SU}, at={[xshift=-6mm]EVa.left}, anchor=right, angle=45}
    \sankeydubins[minimum radius=6mm,ice-to-air]{SU}{SUa}; \sankeyend[air]{SUa}
    \node[font=\tiny, anchor=west] at ([yshift=4mm,xshift=\yoff]SUa.west) {\qq{SUa}: \Lab{vSU}};

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML}, at={[xshift=-15mm,yshift=-\yoff]MLi.south}, anchor=right}
      \sankeyadvance{ML}{1mm} \sankeydubins{ML}{MLi}
      \draw[<-,gray] ([xshift=-2mm]ML.west) -- ++(-10mm,0)
      node[left,font=\tiny,anchor=east,text=black] {Mass loss: \Q{vML}};
    }{ % mass gain
      \sankeyturnleft{MG}{-15} \sankeyadvance{MG}{10mm} % \sankeyturnleft{MG}{15}
      \draw[<-,gray] ([xshift=1mm]MG.east)
      .. controls +(5mm,0) and +(0,0mm) .. ++(5mm,-5mm)
      node[below,font=\tiny,text=black] {Mass gain: \qq{MG}};
    }

>>>>

    \newcommand\labelleft[1]{ % valname
      \node[font=\small, anchor=east]
      at ([yshift=0mm,xshift=-3mm]#1.center) {\Lab{v#1}: \qq{#1}};
    }
    \newcommand\labelright[2]{ % valname
      \node[font=\small, anchor=west]
      at ([yshift=0mm,xshift=3mm]#1.center) {\qq{#1}: \Lab{#2}};
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vGZRET}/GZ, \Q{vBMB}/BMB}
    }{ % mass gain edge case (AQ_east)
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/RUEV,
        \Q{vCALV}/CALV, \Q{vFRONTMELT}/FRONTMELT, \Q{vSHELFMELT}/SHELFMELT,
        \Q{vGZRET}/GZ, \Q{vBMB}/BMB, \Q{vMG}/MG}
    }
    \sankeyturnleft{RFZo}{1}
    \sankeydubins[minimum radius=5mm,ice-to-water-vert]{RFZo}{RFZi}
    \node[font=\small, anchor=east]
           at ([yshift=+4.5mm,xshift=5mm]RFZo.north) {\Lab{vRFZ}: \qq{RFZi}};

@@

    %% SMB outputs
    \sankeynode{name=RUEVa, quantity=\qq{RUEV}, at={[yshift=\yoff]CALVa.left}, anchor=right}
    \sankeyoutin[ice-to-water]{RUEV}{RUEVa}
    \sankeyfork{RUEVa}{\Q{vEV}/EV, \Q{vRU}/RU}
    \sankeynode{name=EVa, quantity=\qq{EV},
      at={[yshift=\yoff,xshift=5mm]RUEVa.left}, anchor=left, angle=45}
    \sankeyoutin[water-to-air]{EV}{EVa}; \sankeyadvance[air]{EVa}{1mm}
    \sankeyend[air]{EVa};
    \node[font=\small, anchor=west] at ([yshift=0mm,xshift=\yoff]EVa.west) {\qq{EVa}: \Lab{vEV}};

@@

    \sankeynode{name=SUa, quantity=\qq{SU}, at={[xshift=-6mm]EVa.left}, anchor=right, angle=45}
    \sankeydubins[minimum radius=6mm,ice-to-air]{SU}{SUa}; \sankeyend[air]{SUa}
    \node[font=\small, anchor=west] at ([yshift=4mm,xshift=\yoff]SUa.west) {\qq{SUa}: \Lab{vSU}};

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML}, at={[xshift=-15mm,yshift=-\yoff]MLi.south}, anchor=right}
      \sankeyadvance{ML}{1mm} \sankeydubins{ML}{MLi}
      \draw[<-,gray] ([xshift=-2mm]ML.west) -- ++(-10mm,0)
      node[left,font=\small,anchor=east,text=black] {Mass loss: \Q{vML}};
    }{ % mass gain
      \sankeyturnleft{MG}{-15} \sankeyadvance{MG}{10mm} % \sankeyturnleft{MG}{15}
      \draw[<-,gray] ([xshift=1mm]MG.east)
      .. controls +(5mm,0) and +(0,0mm) .. ++(5mm,-5mm)
      node[below,font=\small,text=black] {Mass gain: \qq{MG}};
    }
